intRo

### 2015-08-11 jsm-2015/andee/index.Rmd
small changes

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare"
date: "August 11, 2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

@@

## Special thanks
Dr. Cook, for guiding many of the features and interface decisions, and helping test the functionality in preparation for STAT 201

>>>>

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare <br/> Iowa State University"
date: "August 11, 2015 <br> http://j.mp/intRo-JSM2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

@@
